---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# financer

<!-- badges: start -->
<!-- badges: end -->

The goal of financer is to retrieve (free) financial information of companies
from several websites using R.

## Installation

You can install the development version of financer from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("montecapital/financer")
```

## Example

This is a basic example which shows you how to retrieve information
of Illumina Inc. Use [Yahoo Finance](https://finance.yahoo.com/) for basic
information:

```{r example_yahoo}
library(financer)

# tiker of Illumina Inc.
tikr = "ILMN"

# Overview
ilmn.ovrw = yahoo_scrape("ILMN")
ilmn.ovrw[[2]]

# Key-statistics
ilmn.stat = yahoo_scrape("ILMN", page = "key-statistics", ntable = "all")
# Valuation measures
ilmn.stat[[1]]

# Analysis page
ilmn.anal = yahoo_scrape("ILMN", page = "analysis", ntable = "all")
# Expected revenues
ilmn.anal[[2]]

```

Go to [Morningstar](https://www.morningstar.com/) for more detail information
such as the 5-Year financial reports:

```{r example_morning}

# NASDAQ: Stock exchange in which Illumina operates
mrkt = "XNAS"

# Get the Income Statement
ilmn.is = morning_report(tikr, mrkt, "is")
# Extract the revenue
ilmn.is["Revenue",]

# Get the Balance Sheet
ilmn.bs = morning_report(tikr, mrkt, "bs")
# Extract cash and cash equivalents
ilmn.bs["Cash_and_cash_equivalents",]

# Get the Cash Flow
ilmn.cf = morning_report(tikr, mrkt, "cf")
# Show the free cash flow
ilmn.cf["Free_cash_flow",]

```

Or you can inspect the key ratios:

```{r}
# get the key ratios
ilmn.kr = morning_keyratios("ILMN", "XNAS")
# print growth
head(ilmn.kr[[4]])
```

If looking good, visit [Quick FS](https://quickfs.net/) for a 10-Year financial
report. It requires a subscription, but the free version offers 500 requests
a day:

```{r example_quickfs}

# Illumina operates in the US
country = "US"

# check current quota
quickfs_quota()

# get the statements
ilmn.fstat.long = quickfs_getstatement("ILMN", "US")
ilmn.fstat.long$finances$finances_ts["revenue",]

# financial statements "cost" 10 points
quickfs_quota()

```

## Disclaimer

This is a personal project and doesn't come with any guarantee.
